# Analysis

```{r, cache=TRUE, echo=FALSE,  warning=FALSE}
  library(ggplot2)
  theme_set(theme_minimal())

  library(purrr)
  library(pracma)
  library(plyr)
  library(dplyr)
  library(stringr)
  library(latex2exp)
  library(scales)
  library(repr)

  options(repr.plot.width=4, repr.plot.height=3)

  df <- read.csv("internal-control-experiments.csv")
  df$iteration=factor(df$iteration)
  which.nonnum <- function(x) {
    which(is.na(suppressWarnings(as.numeric(as.character(x)))))
  }

  df$time=as.POSIXct(df$time/1000000, origin="1970-01-01")
  unique(df$name)
  unique(df$variable)
  pStatic=200
```

```{r}
  df_control = df[which(df["name"] == "controlOn"),]
  df_random = df[which(df["name"] == "randomUniform"),]
```

# Total energy expenditure
```{r}
  df_rapl0 = df[which(df$variable == "sensor-RaplKey (PackageID 0)"), c("name","value","iteration","time")]
  df_rapl0$value=as.numeric(as.character(df_rapl0$value))
  df_rapl1 = df[which(df$variable == "sensor-RaplKey (PackageID 1)"), c("name","value","iteration","time")]
  df_rapl1$value=as.numeric(as.character(df_rapl1$value))
  df_rapl = merge( df_rapl0, df_rapl1,by=c("time","iteration","name"))
  df_rapl = rename(df_rapl, rapl0 = value.x, rapl1 = value.y)
  df_rapl$value = df_rapl$rapl0 + df_rapl$rapl1 + pStatic
  integrateWattHours <- function(ts,vs) {
    return(tail(cumtrapz(as.numeric(ts)/3600,vs),n=1))
  }
  df_rapl = ddply(df_rapl, .(name,iteration), summarize, wh=integrateWattHours(time,value))
  print(df_rapl)
```

# Total progress reporting
```{r}
  df_progress = df[which(df$variable == "sensor-sensor-Downstream")
                  , c("name","value","iteration")]
  df_progress$value=as.numeric(as.character(df_progress$value))
  df_progress = ddply(df_progress, .(name,iteration), summarize, instructions=mean(value), instructionsSd = sd(value) )
  print(df_progress)
```

# Runtimes
```{r}
  df_runtime = df[which(grepl("sensor",df$variable) & df$variable != "actionType"), c("name","iteration","time")]
  df_runtime = ddply(df_runtime, .(name,iteration), summarize, runtime=as.numeric(max(time),units="secs"))
  print(df_runtime)
```

# Global stats.
```{r}
  df_post = df_runtime %>%
    full_join(.,df_rapl,by=c("name","iteration")) %>%
    full_join(.,df_progress,by=c("name","iteration"))

  print(df_post)

  df_reference= filter(df_post, name == "pcap250/250")
  print(df_reference)
  runtime_reference = mean(df_reference$runtime)
  throughput_reference = mean(df_reference$instructions)
  df_post$constraintBreach = df_post$runtime > (1.1 * runtime_reference)
  print(df_post)
```


# Average total watt-hour energy expenditure by strategy
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df_post, aes(x=name, y=wh) ) +
    geom_boxplot()

```

# Average runtime by  strategy
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df_post, aes(x=name, y=runtime) ) +
    geom_boxplot() +
    geom_hline(yintercept = runtime_reference/0.9, linetype="dashed", color = "red") +
    geom_hline(yintercept = runtime_reference, linetype="dashed", color = "black")
```

# Average throughput by strategy
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df_post, aes(x=name, y=instructions) ) +
    geom_boxplot() +
    geom_hline(yintercept = 0.9 * throughput_reference, linetype="dashed", color = "red") +
    geom_hline(yintercept = throughput_reference, linetype="dashed", color = "black")
```

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df_post, aes(x=name, y=instructionsSd) ) +
    geom_boxplot()
```

# Average power by strategy
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df_post, aes(x=name, y=wh/runtime) ) +
    geom_boxplot()
```

# Sensor outputs for static high and low powercap

Package 0:

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df[which((df$name=="pcap250/250" |df$name=="pcap100/100"|df$name=="pcap100/250"|df$name=="pcap250/100") & df$variable=="sensor-RaplKey (PackageID 0)" ) ,],
         aes(time, as.numeric(as.character(value)),group=name,color=name) )+
    geom_point() +
    geom_line() +
    facet_grid(rows = vars(iteration), scales="free_y") +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    ylab("RAPL Sensor: Package 0 (Watts)")

```

Package 1:

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df[which((df$name=="pcap250/250" | df$name=="pcap100/100"|df$name=="pcap100/250" | df$name=="pcap250/100") & df$variable=="sensor-RaplKey (PackageID 1)" ) ,],
         aes(time, as.numeric(as.character(value)),group=name,color=name) )+
    geom_point() +
    geom_line() +
    facet_grid(rows = vars(iteration), scales="free_y") +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0)) +
    ylab("RAPL Sensor: Package 1 (Watts)")
```

Downstream perf monitoring:

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(data=df[which((df$name=="pcap250/250" |df$name=="pcap100/100") & df$variable=="sensor-sensor-Downstream" ) ,],
         aes(time, as.numeric(as.character(value)),group=name,color=name) )+
    geom_point() +
    geom_line() +
    facet_grid(rows = vars(iteration), scales="free_y") +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    ylab("Instruction rate: IPS")

```


# Bandits

## Meta-Action type
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=2}
  ggplot(df_control[which(df_control["variable"] == "actionType"),], aes(x=time, y=as.character(value), group=iteration,color=iteration) )+
    geom_point() +
    facet_grid(rows = vars(variable),scales="free_y") +
    scale_x_datetime() +
    theme(strip.text.y = element_text(angle =0))
```


## Sensor outputs
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=5}
  ggplot(df_control[which(grepl("sensor",df_control$variable)),],
         aes(x=time, y=as.numeric(as.character(value)), group=iteration,color=iteration) )+
    geom_line() +
    geom_point() +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0)) +
    facet_grid(rows = vars(variable),scales="free_y") +
    xlab("t") +
    ylab("sensor")
```



## Objectives (RAPL sensors)
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=4}
  ggplot(df_control[which(grepl("objective",df_control$"variable")),],
         aes(x=time, y=as.numeric(as.character(value)), group=iteration,color=iteration) )+
    geom_line() +
    geom_point() +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0)) +
    facet_grid(rows = vars(variable))
```

## Pull counts
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(df_control[which(grepl("pulls",df_control$"variable")),],
         aes(x=time, y=as.numeric(as.character(value)), group=variable,color=variable) )+
    geom_line() +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration))
```

## Average loss evolution.
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=8}
  df_loss = df_control[which(df_control["variable"] == "loss"),]
  ggplot(df_loss,
         aes(x = time,
             y = cumsum(as.numeric(as.character(value))) / as.numeric(time,unit="sec"),
             group=iteration,
             color=iteration))+
    geom_line() +
    scale_x_datetime()+
    facet_grid(rows = vars(variable),scales="free_y") +
    theme(strip.text.y = element_text(angle =0)) +
    xlab("t") +
    ylab("average loss")
```

## Internal bandit parameters
```
  ggplot(df_control[which(grepl("proba",df_control$"variable")),],
         aes(x=time, y=as.numeric(as.character(value)), group=variable,color=variable) )+
    geom_line() +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration),scales="free_y")+
    ylab("pull probabilities")
```

```
  ggplot(df_control[which(grepl("cumulativeLoss",df_control$"variable")),],
         aes(x=time, y=as.numeric(as.character(value)), group=variable,color=variable) )+
    geom_line() +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration),scales="free_y")+
    ylab("cumulative losses")

```

## Average observed constraints.
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=12}
  ggplot(df_control[which(grepl("avgCst",df_control$"variable")),],
         aes(x=time, y=as.numeric(as.character(value)), group=variable,color=variable) )+
    geom_line() +
    scale_x_datetime()+
    geom_hline(yintercept = 1/0.9, linetype="dashed", color = "red") +
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration))
```

## Average observed objs
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=4}
  ggplot(df_control[which(grepl("avgObj",df_control$"variable")),],
         aes(x=time, y=as.numeric(as.character(value)), group=variable,color=variable) )+
    geom_line() +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration))
```

# Randomized strategy

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  unique(df_random$variable)
  summary(df_random)
```


## Pull counts
```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=3}
  ggplot(df_random[which(grepl("pulls",df_random$"variable")),],
         aes(x=time, y=as.numeric(as.character(value)), group=variable,color=variable) )+
    geom_line() +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration))
```

## online sensor averages

### Throughputs (arm values)

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=6}
  df1=df_control[which(grepl("avgMeasurement-Downstream",df_control$"variable")),]
  df2=df_control[which(grepl("avgRef-Downstream",df_control$"variable")),]
  df1$tag="measurements"
  df2$tag="references"
  df=rbind(df2,df1)
  df$variable=gsub("avgRef-","",df$variable)
  df$variable=gsub("avgMeasurement-","",df$variable)
  df$variable=factor(df$variable)
  df$value = as.numeric(as.character(df$value))

  ggplot(df) +
    geom_line(aes(x=time, y=value, linetype=tag, color=variable, group=interaction(variable,tag))) +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration))
```

### Package 0 (arm values)

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=6}
  df1=df_control[which(grepl("avgMeasurement-RaplKey \\(PackageID 0",df_control$"variable")),]
  df2=df_control[which(grepl("avgRef-RaplKey \\(PackageID 0",df_control$"variable")),]
  df1$tag="measurements"
  df2$tag="references"
  df=rbind(df2,df1)
  df$variable=gsub("avgRef-","",df$variable)
  df$variable=gsub("avgMeasurement-","",df$variable)
  df$variable=factor(df$variable)
  df$value = as.numeric(as.character(df$value))

  ggplot(df) +
    geom_line(aes(x=time, y=value, linetype=tag, color=variable, group=interaction(variable,tag))) +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration))
```

### Package 1 (arm values)

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=6}
  df1=df_control[which(grepl("avgMeasurement-RaplKey \\(PackageID 1",df_control$"variable")),]
  df2=df_control[which(grepl("avgRef-RaplKey \\(PackageID 1",df_control$"variable")),]
  df1$tag="measurements"
  df2$tag="references"
  df=rbind(df2,df1)
  df$variable=gsub("avgRef-","",df$variable)
  df$variable=gsub("avgMeasurement-","",df$variable)
  df$variable=factor(df$variable)
  df$value = as.numeric(as.character(df$value))

  ggplot(df) +
    geom_line(aes(x=time, y=value, linetype=tag, color=variable, group=interaction(variable,tag))) +
    scale_x_datetime()+
    theme(strip.text.y = element_text(angle = 0))+
    facet_grid(rows = vars(iteration))
```

## Internal values (debugging)

### objective computations

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=12}
  ggplot(df_control[which(grepl("reportEvaluatedObjectives|sensor", df_control$variable)),],
         aes(x=time, y=as.numeric(as.character(value)), group=iteration,color=iteration) )+
    geom_line() +
    geom_point() +
    scale_x_datetime()+
    facet_grid(rows = vars(variable),scales="free_y") +
    theme(strip.text.y = element_text(angle = 0)) +
    xlab("t") +
    ylab("hco")
```

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=6}
  ggplot(df_control[which(grepl("reportNormalizedObjectives", df_control$variable)),],
         aes(x=time, y=as.numeric(as.character(value)), group=iteration,color=iteration) )+
    geom_line() +
    geom_point() +
    scale_x_datetime()+
    facet_grid(rows = vars(variable),scales="free_y") +
    theme(strip.text.y = element_text(angle = 0)) +
    xlab("t") +
    ylab("hco")
```

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=12}
  ggplot(df_control[which(grepl("reportEvaluatedConstraints", df_control$variable)),],
         aes(x=time, y=as.numeric(as.character(value)), group=iteration,color=iteration) )+
    geom_line() +
    geom_point() +
    scale_x_datetime()+
    facet_grid(rows = vars(variable),scales="free_y") +
    theme(strip.text.y = element_text(angle = 0)) +
    xlab("t") +
    ylab("hco")
```


## pure bandit plots

```{r, cache=TRUE, echo=FALSE, fig.cap="", dev="pdf", fig.width=11, fig.height=6}
  ggplot(df_control[which(df_control$variable == "constraint-0" | df_control$variable == "objective-0"),],
         aes(x=time, y=as.numeric(as.character(value)), group=iteration,color=iteration) )+
    geom_line() +
    scale_x_datetime()+
    facet_grid(rows = vars(variable),scales="free_y") +
    geom_hline(yintercept = (1.0/1.1), linetype="dashed", color = "red") +
    theme(strip.text.y = element_text(angle = 0)) +
    xlab("t") +
    ylab("hco")
```
